\documentclass[a4paper, 11pt, oneside]{memoir}

\usepackage{newpxtext,newpxmath}
\usepackage[hidelinks]{hyperref}

\usepackage{enumitem}

\usepackage{siunitx}
\usepackage[style=authoryear-comp, sorting=ydnt, giveninits=true, backend=biber,
            useprefix=true, uniquename=false, uniquelist=false,
            maxnames=2, maxbibnames=8, natbib]{biblatex}
  \renewbibmacro{in:}{%
    \ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}%
  }
  \addbibresource{mypub.bib}


%%% Memoir class style customizations %%%

% Page and margin settings
\setlrmarginsandblock{0.85in}{0.85in}{*}
\setulmarginsandblock{0.85in}{0.85in}{*}
\checkandfixthelayout 

% Header and footer
\copypagestyle{cv}{plain}
\makeoddfoot{cv}{Dimas A.~A.~Dutra}{\textit{Curriculum Vitae}}{\thepage}
\pagestyle{cv}

% Sectioning
\setsecnumdepth{book}
\newcommand{\ruledsec}[1]{%
  \Large\scshape\raggedright #1 \par\vspace{-1ex}\noindent\hrulefill
}
\setsecheadstyle{\ruledsec}

\begin{document}
\thispagestyle{plain}

\begin{center}
  {
    \LARGE \bfseries \scshape 
    Dimas Abreu Archanjo Dutra
  }
  \\[1ex]
  \small
  \texttt{\href{mailto:dimas.dutra@mail.wvu.edu}{dimas.dutra@mail.wvu.edu}}
  \itshape\qquad
  +1~(304)~777-9325
  \\
  1306 Evansdale Drive, Morgantown, WV, 26506-6106
\end{center}

\section{Current Positions}

\begin{description}
\item \textbf{Assistant Professor} (on leave), 
  Department of Mechanical Engineering
  \hfill 2015--present
  \\
  Universidade Federal de Minas Gerais (UFMG), Brazil.

\item \textbf{Postdoctoral Fellow}, 
  Department of Mechanical and Aerospace Engineering
  \hfill 2021--present
  \\
  West Virginia University (WVU), Morgantown, WV.
\end{description}

\section{Education}
\begin{description}
\item Ph.D. in Electrical Engineering \hfill 2011--2014
  \\
  Universidade Federal de Minas Gerais (UFMG), Brazil
  \\
  \emph{Dissertation:} Maximum \emph{a posteriori} joint state path and
  parameter estimation in stochastic differential equations.
  \emph{Advisors:} Luis Antonio Aguirre and Bruno Otávio Soares Teixeira.

\item B.Sc. in Control and Automation Engineering
  \hfill 2005--2010
  \\
  Universidade Federal de Minas Gerais (UFMG), Brazil
  \\
  \textit{Senior thesis:} System identification of a light aircraft.
  \emph{Advisor:} Luis Antonio Aguirre.
\item Foreign Exchange Student \hfill 2009--2010
  \\
  University of Wisconsin--Madison, College of Engineering
\item Technical High School: Industrial Instrumentation \hfill 2002--2004
  \\
  Colégio Técnico do Centro Pedagógico da UFMG (Coltec), Brazil
\end{description}

\section{Research and teaching interests}
\begin{tabular}{lll}
  State Estimation & Robotics & Control Theory
  \\
  System Identification & Optimization & Bayesian Inference
\end{tabular}

\section{Faculty training and technical workshops}
\begin{description}
\item Write Winning Grant Proposals \hfill 2021
  \\
  Grant Writers' Seminars and Workshops, LLC, 7 hours.
\item Teaching for Higher Education: Evaluation and meaningful learning
  \hfill 2020
  \\
  UFMG Teaching Methodologies and Innovation Directorate, 60 hours.
\item Teaching for Higher Education Development Course \hfill 2011
  \\
  UFMG Teaching Methodologies and Innovation Directorate, 60 hours.
\item Workshop on Flight Data and System Identification \hfill 2013
  \\
  By Ravindra V.~Jategaonkar of the German Aerospace Center (DLR), 4 days
\end{description}

\section{Selected list of publications}
\nocite{*}

\subsection{Journal Papers}
\printbibliography[
  type=article, heading=none,
]

\subsection{Conference Papers}
\printbibliography[
  type=inproceedings, heading=none,
]

\section{Citation database profiles}
\begin{description}
\item[Google Scholar] 
  \url{https://scholar.google.com/citations?user=3c_a2awAAAAJ}\newline
  Publications:~10, Citations:~37, H-index:~4,
\item[Publons]
  \url{https://publons.com/researcher/AAF-9208-2020}\newline
  Publications:~8, Citations:~14, H-index:~3, Verified Reviews:~13, 
  Excellent Reviewer
\item[Scopus]
  \url{https://www.scopus.com/authid/detail.uri?authorId=24775609400}\newline
  Publications:~7, Citations:~28, H-index:~3
\item[ORCID]
  \url{https://orcid.org/0000-0001-8202-744X}\newline
  Publications:~8
\end{description}

\noindent
Citation counts and metrics accessed January~9, 2022.

\clearpage
asfdsadfs


\end{document}
